---
title: "Multi-area Grid Metrics Analyzer"
author: "Created by: National Renewable Energy Laboratory (NREL)"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path=fig.path.name, dev='png')

# Set dynamic height for figure in regional generation chunk
if (exists('zone.names')) { 
  f.height = max(( length(zone.names) %/% 3 + length(zone.names) %% 3 ) * 5,5)
  } else { f.height = 5 }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Data below generated for:
"`r gsub('.*Model', 'Model', db$filename)`"

***
## Annual Dispatch Stacks 
***
## 1. Total Generation
```{r total-gen-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_total_gen_stack.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 2. Zonal Generation
```{r zone-gen-stacks, fig.height=f.height, fig.width=10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_zone_gen_stacks.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 3. Regional Generation
```{r region-gen-stacks, resize.height=F, fig.height=f.height, fig.width=10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_region_gen_stacks.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 4. Individual Regions
```{r individual-region-stacks, include=FALSE, fig.height=8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(individual.region.stacks.log) {
  if ( typeof(total.generation)=='character' ) {
    print('ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('ERROR: total.avail.cap has errors. Cannot run this section.')
  } else if ( typeof(r.load) == 'character' ) {
    print('ERROR: region_load function not returning correct results. Cannot run this section')
  } else { 
    # Query region and zonal generation
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR') } )
    # If the regional query didn't work, return an error. Else create the plots by calling the markdown file.
    if ( typeof(r.z.gen)=='character' ) {
      print('ERROR: region_zone_gen function not returning correct results.')
    } else {
      plot.regions = region.names[!region.names %in% ignore.regions]
      key.plots = lapply(plot.region, function(r){
                         knit_expand(file = 'source_scripts/p_individual_region_stacks.Rmd', region.name=r)
                         })
      # Reconstruct the plot data into a format that will be output into the HTML below
      individual.region.stacks = knit_child(text = unlist(key.plots))
      }
    }
} else { individual.region.stacks = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r individual.region.stacks`


***
## 5-7. Specified Period Dispatch Stacks
``` {r key-period-dispatch, cache=FALSE, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (key.period.dispatch.total.log | key.period.dispatch.zone.log | key.period.dispatch.region.log){  

  # Call interval_gen function and proces data for plots
  source('source_scripts/d_key_period_dispatch.R')

  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('key.period.gen') ) {
  # Check to see if the right data is ready for plotting.
    if ( typeof(key.period.gen)=='character' ) {
      key.period.dispatch.total  = 'ERROR: interval_gen function not returning correct results.'
      key.period.dispatch.zone   = 'ERROR: interval_gen function not returning correct results.'
      key.period.dispatch.region = 'ERROR: interval_gen function not returning correct results.'
    } else {
      # Create data if total database info was selected in input file.
      if (key.period.dispatch.total.log) {
        key.plots.total = lapply(period.names, function(p){
          knit_expand(file = 'source_scripts/p_key_period_dispatch_total.Rmd', period.name = p)
          })
        key.period.dispatch.total = knit_child(text = unlist(key.plots.total))
      } else {key.period.dispatch.total  = 'Section not run according to input file.'}
        
      # Create data if zonal dispatch stacks were selected in input file.
      if (key.period.dispatch.zone.log) {
          key.plots.zone = mapply(function(p,z){knit_expand(file = 'source_scripts/p_key_period_dispatch_zone.Rmd', 
                                                            period.name = p, zone.name = z)},
                                  rep(period.names,length(zone.names)), rep(zone.names,each=n.periods))
        key.period.dispatch.zone = knit_child(text = unlist(key.plots.zone))
      } else {key.period.dispatch.zone   = 'Section not run according to input file.'}
        
      # Create data if regional dispatch stacks were selected in input file.
      if (key.period.dispatch.region.log) {
        key.plots.region = mapply(function(p,r){knit_expand(file = 'source_scripts/p_key_period_dispatch_region.Rmd', 
                                                            period.name = p, region.name = r)},
                                  rep(period.names,length(region.names)), rep(region.names,each=n.periods))
        key.period.dispatch.region = knit_child(text = unlist(key.plots.region))
      } else {key.period.dispatch.region = 'Section not run according to input file.'}        
    }
  } else {
    key.period.dispatch.total  = 'Problem sourcing or running d_key_period_dispatch.R.'
    key.period.dispatch.zone   = 'Problem sourcing or running d_key_period_dispatch.R.'
    key.period.dispatch.region = 'Problem sourcing or running d_key_period_dispatch.R.'
  }
} else { key.period.dispatch.total  = 'Section not run according to input file.'
         key.period.dispatch.zone   = 'Section not run according to input file.' 
         key.period.dispatch.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### 5. Total
`r key.period.dispatch.total`

***
### 6. Zones
`r key.period.dispatch.zone`

***
### 7. Regions
`r key.period.dispatch.region`

***
## 8-9. Curtailment
***
### 8. Average Daily Curtailment
```{r yearly-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_daily_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 9. Average Interval Curtailment
```{r daily-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_interval_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 10. Total Gen
```{r annual-generation-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (annual.generation.table){
  # If the data doesn't already exist, run the query function.
  if ( !exists('yr.gen') ) {
    yr.gen = tryCatch(gen_by_type(total.generation, total.avail.cap), 
                      error = function(cond) { return('ERROR: gen_by_type function not returning correct results') } ) 
  }
  # Set the order level that generatino type will be displayed.
  yr.gen[, Type := factor(Type, levels = c(gen.order))] 
  setorder(yr.gen,Type)
  
  # Separate out curtailment from generation
  curt = yr.gen[Type=='Curtailment', ]
  yr.gen = yr.gen[Type!='Curtailment', ]
  
  # Calculate the percent generation of each type, and percent curtailment
  yr.gen[, Total:=sum(GWh)]
  yr.gen[, Percent:=GWh/Total*100]
  yr.gen[, Total:=NULL]
  curt[, Total:=GWh+yr.gen[Type %in% re.types, sum(GWh)] ]
  curt[, Percent:=GWh/Total*100]
  curt[, Total:=NULL]
  
  # combine back into one table. 
  yr.gen = rbindlist(list(yr.gen, curt))
  row.names(yr.gen) = NULL
  kable(yr.gen, format.args = list(big.mark = ','), digits=2) 
  } else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 11. Total Costs
```{r annual-cost-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.cost.table) {
  # Run the cost query function
  cost.table = tryCatch( costs(total.emissions.cost, total.fuel.cost, total.ss.cost, total.vom.cost), 
                         error = function(cond) { return('ERROR: costs function not returning correct results.') })
  kable(cost.table, format.args = list(big.mark = ','))
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 12. Region and Zone Info (GWh)
``` {r region-flow-tables, results = 'asis'}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.flow.table) {
  # Query region and zone stats.
  r.stats = tryCatch( region_stats(total.region.load, total.region.imports, total.region.exports, total.region.ue), 
                      error = function(cond) { return('ERROR: region_stats function not returning correct results.') })
    # Set names if data exists
  if ( !typeof(r.stats)=='character' ) { 
    setnames(r.stats, 'name', 'Region Name')
  } else{ print("ERROR: region_stats not returning correct results")}
  # Print data. Will print error message if errors
  kable(r.stats, format.args = list(big.mark = ','), digits=2)
  } else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

``` {r zone-flow-tables, results = 'asis'}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.flow.table) {
  # Query region and zone stats.
  z.stats = tryCatch( zone_stats(total.region.load, total.region.imports, total.region.exports, total.region.ue, 
                                 total.zone.load, total.zone.imports, total.zone.exports, total.zone.ue), 
                      error = function(cond) { return('ERROR: zone_stats function not returning correct results.') })
  # Set names if data exists
  if ( !typeof(z.stats)=='character' ) { 
    setnames(z.stats, 'name', 'Zone Name')
  } else{ print("ERROR: region_stats not returning correct results")}
  # Print data. Will print error message if errors
  kable(z.stats, format.args = list(big.mark = ','), digits=2)
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 13. Interface Flow Table
```{r interface-flow-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(interface.flow.table) {
  # Call the query function to get interface flows for the interfaces selected in the input file.
  interface.flows = tryCatch( annual_interface_flows(total.interface.flow), 
                              error=function(cond) {return('ERROR: interface_flows query not returning correct results.')})
  # Print data 
  kable(interface.flows, digits=3)
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 14. Interface Flow Plots
```{r interface-flow-plots, resize.width=T, fig.width=10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_interface_flow.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 15. Specified Period Interface Flow Plot
```{r key-period-interface-flow-plots, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (key.period.interface.flow.plots) {

  # Pull out interface flow data for only specified periods in input file
  source('source_scripts/d_key_period_interface_flow.R')
  
  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('plot.flows') ) {
    # Check to see if the right data is ready for plotting.
    if ( typeof(plot.flows)=='character' ) {
      print('ERROR: interval_interface_flows function not returning correct results.')
    } else {        
      # Create data for each plot for the interesting periods
      key.plots = lapply(period.names, function(p){
                         knit_expand(file = 'source_scripts/p_key_period_interface_flow.Rmd', period.name = p)
                         }) 
      # Reconstruct the plot data into a format that will be output into the HTML below
      key.period.interface.flow = knit_child(text = unlist(key.plots))
   
    }
  } else { key.period.interface.flow = 'Problem sourcing or running d_key_period_interface_flow.R.' }
  
} else { key.period.interface.flow = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r key.period.interface.flow`

***
## 16-17. Reserves
***
### 16. Annual Reserve Provisions and Shortage
```{r annual-reserves-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if(annual.reserves.table) {
  # Call the query function to get annual reserve amounts.
  annual.reserves = tryCatch( annual_reserves(total.reserve.provision, total.reserve.shortage), 
                              error = function(cond) { return('ERROR: annual_reserves function not returning correct results.') })
  if(typeof(annual.reserves)!='character') { 
    if(length(unique(annual.reserves$scenario))>1){
      kable(annual.reserves, format.args = list(big.mark = ',')) 
    } else{
      kable(annual.reserves[, .(Type, `Provisions (GWh)`, `Shortage (GWh)`)], format.args = list(big.mark = ',')) 
    }
  } else { print('ERROR: annual_reserves is not returning correct results.')}
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 17. Average Interval and Daily Reserve Provisions
```{r reserves-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_reserves.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 18. Region and Zone Generation (GWh)
```{r region-gen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.gen.table) {
  if (typeof(r.load)=='character' ) {
    print('ERROR: r.load not correct. Cannot run this section.')
  } else{
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: region_zone_gen function not returning correct results.') } )
    if ( typeof(r.z.gen)=='character' ) { 
      r.gen.table = 'ERROR: region_zone_gen function not returning correct results.'
    } else {
      r.z.gen[, Type := factor(Type, levels = gen.order)] # Reassign the order which the generation type will be displayed.
      
      # Sum regional generation by type
      r.gen.table = r.z.gen[, .(GWh = sum(GWh)), by=.(Region, Type)] %>%
        dcast.data.table(Region~Type, value.var = 'GWh')
      r.gen.table[is.na(r.gen.table)] = 0
      region.load = r.load[, .(Region, Load = value)]
      setkey(region.load,Region)
      setkey(r.gen.table,Region)
      r.gen.table = r.gen.table[region.load]
    }
    # Print results
    kable(r.gen.table, digits=2, format.args = list(big.mark = ','))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
```{r zone-gen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (region.zone.gen.table) {
  if (typeof(z.load)=='character' ){
    print('ERROR: z.load not correct. Cannot run this section.')
  } else{
    r.z.gen = tryCatch( region_zone_gen(total.generation, total.avail.cap), 
                        error = function(cond) { return('ERROR: region_zone_gen function not returning correct results.') } )
    if ( typeof(r.z.gen)=='character' ) { 
      z.gen.table = 'ERROR: region_zone_gen function not returning correct results.'
    } else {
      r.z.gen[, Type := factor(Type, levels = gen.order)] # Reassign the order which the generation type will be displayed.
      
      # Sum zonal generation by type
      z.gen.table = r.z.gen[, .(GWh = sum(GWh)), by=.(Zone, Type)] %>%
        dcast.data.table(Zone~Type, value.var = 'GWh')
      z.gen.table[is.na(z.gen.table)] = 0
      zone.load = z.load[, .(Zone, Load = value)]
      setkey(zone.load,Zone)
      setkey(z.gen.table,Zone)
      z.gen.table = z.gen.table[zone.load]
    }
    # Print results
    kable(z.gen.table, digits=2, format.args = list(big.mark = ','))
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 19. Capacity Factors
```{r capacity-factor-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if(capacity.factor.table) {
  if ( typeof(total.generation)=='character' ) {
    print('ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.installed.cap) == 'character' ) { 
    print('ERROR: total.installed.cap has errors. Cannot run this section.')
  } else{
    # Call the query function to get capacity factor.
    cf = tryCatch( capacity_factor(total.generation, total.installed.cap), 
                   error = function(cond) { return('ERROR: capacity_factor function not returning correct results.') })
    kable(cf, format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 20. Region Price Duration Curves
```{r price-duration-curve, fig.width = 10}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/p_price_duration_curve.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 21-22. DA-RT Committment and Dispatch Plots
```{r committment-dispatch, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (commit.dispatch.region | commit.dispatch.zone) {
  
  source('source_scripts/d_DA_RT_commit_dispatch.R') # Call this R script which created the data needed for plotting.
  
  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('plot.data.all') ) {
    # Check to see if the right data is ready for plotting.
    if ( typeof(plot.data.all)=='character' ) {
      print('ERROR: cap_committed function not returning correct results.')
    } else {
      # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
      if (commit.dispatch.zone) {
        da.rt.zone = mapply(function(p,z){knit_expand(file = 'source_scripts/p_DA_RT_commit_dispatch_zone.Rmd', 
                                                      period.name = p, zone.name = z)},
                            rep(period.names,length(zone.names)), rep(zone.names,each=n.periods))
        da.rt.zone = knit_child(text = unlist(da.rt.zone))
      } else {da.rt.zone = 'Section not run according to input file.'}
      
      # Check if regional DA-RT plots were selected in input file. If so create a plot for each region
      if (commit.dispatch.region) {  
        da.rt.region = mapply(function(p,r){knit_expand(file = 'source_scripts/p_DA_RT_commit_dispatch_region.Rmd', 
                                                        period.name = p, region.name = r)},
                              rep(period.names,length(region.names)), rep(region.names,each=n.periods))
        da.rt.region = knit_child(text = unlist(da.rt.region))
      } else {da.rt.region = 'Section not run according to input file.'} 
    }
  } else { da.rt.zone = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
         da.rt.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'}
  
} else { da.rt.zone = 'Section not run according to input file.'
         da.rt.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### 21. Zones
`r da.rt.zone`

### 22. Regions
`r da.rt.region`
