---
title: "Multi-area Grid Metrics Analyzer Comparison Plots"
author: "Created by: `r Sys.info()['user']`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path=fig.path.name, dev='png', fig.width=12)

# Set dynamic height for figure in regional generation chunk
z.height = ( length(zone.names) %/% 3 + length(zone.names) %% 3 ) * 5
r.height = ( length(region.names) %/% 3 + length(region.names) %% 3 ) * 5
res.height = ( length(reserve.names) %/% 2 + length(reserve.names) %% 2 ) * 5
s.height = ( length(db.loc) ) * 6
p.height = ( length(period.names) %/% 2 + length(period.names) %% 2 ) * 5
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Data below generated for:
"`r gsub('.*Model', 'Model', db$filename)`"

***
## Annual Dispatch Stacks 
***
## 1. Generation Differences
```{r gen-diff-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_diff_gen_stack.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 2. Zonal Generation
```{r zone-gen-diff-stacks, fig.height=z.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  source('source_scripts/compare/c_p_zone_gen_stacks.Rmd')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 3. Regional Generation
```{r region-gen-diff-stacks, fig.height=r.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_region_gen_stacks.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 4-6. Specified Period Dispatch Stacks
``` {r key-period-dispatch, cache=FALSE, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (key.period.dispatch.total.log | key.period.dispatch.zone.log | key.period.dispatch.region.log){  

  # Call interval_gen function and proces data for plots
  source('source_scripts/d_key_period_dispatch.R')

  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('key.period.gen') ) {
  # Check to see if the right data is ready for plotting.
    if ( typeof(key.period.gen)=='character' ) {
      key.period.dispatch.total  = 'ERROR: interval_gen function not returning correct results.'
      key.period.dispatch.zone   = 'ERROR: interval_gen function not returning correct results.'
      key.period.dispatch.region = 'ERROR: interval_gen function not returning correct results.'
    } else {
  
      key.plots.total = list() # Creates empty list for plot data
      key.plots.zone = list() # Creates empty list for plot data
      key.plots.region = list() # Creates empty list for plot data
      r.idx = 1
      z.idx = 1
      
      # Create data for each plot for the interesting periods
      for ( p in 1:n.periods ) {
        period.name = period.names[p]
        
        # Check if total database info was selected in input file.
        if (key.period.dispatch.total.log) {
          key.plots.total[[p]] = knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_total.Rmd', period.name = period.name)
        } else {key.period.dispatch.total  = 'Section not run according to input file.'}
        
        # Check if zonal dispatch stacks were selected in input file.
        if (key.period.dispatch.zone.log) {
          for ( z in 1:length(zone.names) ) {
            zone.name = zone.names[z]
            key.plots.zone[[z.idx]] = knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_zone.Rmd', period.name = period.name, zone.name = zone.name) 
            z.idx = z.idx + 1
          } 
        } else {key.period.dispatch.zone   = 'Section not run according to input file.'}
        
        # Check if regional dispatch stacks were selected in input file.
        if (key.period.dispatch.region.log) {
          for ( r in 1:length(region.names) ) {
            region.name = region.names[r]
            key.plots.region[[r.idx]] = knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_region.Rmd', period.name = period.name, region.name = region.name)
            r.idx = r.idx + 1
          }
        } else {key.period.dispatch.region = 'Section not run according to input file.'}
      }
  
      # Reconstruct the plot data into a format that will be output into the HTML below
      if (key.period.dispatch.total.log) { key.period.dispatch.total = knit_child(text = unlist(key.plots.total)) }
      if (key.period.dispatch.zone.log) { key.period.dispatch.zone = knit_child(text = unlist(key.plots.zone)) }
      if (key.period.dispatch.region.log) { key.period.dispatch.region = knit_child(text = unlist(key.plots.region)) }
    }
  } else {
    key.period.dispatch.total  = 'Problem sourcing or running d_key_period_dispatch.R.'
    key.period.dispatch.zone   = 'Problem sourcing or running d_key_period_dispatch.R.'
    key.period.dispatch.region = 'Problem sourcing or running d_key_period_dispatch.R.'
  }
} else { key.period.dispatch.total  = 'Section not run according to input file.'
         key.period.dispatch.zone   = 'Section not run according to input file.' 
         key.period.dispatch.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Total
`r key.period.dispatch.total`

***
### Zones
`r key.period.dispatch.zone`

***
### Regions
`r key.period.dispatch.region`

***
## 7-9. Curtailment
***
### 7. Total Curtailment Difference
```{r yearly-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_t_diff_curtailment.R')
if(exists('curt.diff')) { kable(curt.diff, format.args = list(big.mark = ','), digits=2) }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 8. Daily Curtailment Difference
```{r daily-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_daily_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 9. Interval Curtailment Difference
```{r interval-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_interval_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 10. Total Cost Differences
```{r annual-cost-difference-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source("source_scripts/compare/c_t_diff_annual_cost.R")
if(exists('cost.diff.table')) { kable(cost.diff.table, format.args = list(big.mark = ',')) }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 12. Region and Zone Info (GWh)
``` {r region-zone-flow-diff-tables}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 13. Interface Flow Table
```{r interface-flow-diff-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 14. Interface Flow Plots
```{r interface-flow-diff-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 16-17. Reserves
***
### 16. Annual Reserve Shortage by Scenario
```{r annual-reserves-scen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_t_total_reserve_shortage.R')
if(exists('res.short.table')) { kable(res.short.table, format.args = list(big.mark = ',')) }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 17. Reserve Provisions by generator type
```{r reserves-stacks, fig.height=res.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source("source_scripts/compare/c_p_reserves_stack.R")
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 20. Region Price Duration Curves
```{r price-duration-curve-scen, fig.height=r.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_price_duration_curve.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 21. DA-RT Committment and Dispatch Plots
```{r committment-dispatch, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (commit.dispatch.region | commit.dispatch.zone) {
  
  source('source_scripts/d_DA_RT_commit_dispatch.R') # Call this R script which created the data needed for plotting.
  
  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('plot.data.all') ) {
    # Check to see if the right data is ready for plotting.
    if ( typeof(plot.data.all)=='character' ) {
      print('ERROR: cap_committed function not returning correct results.')
    } else {
  
      da.rt.zone = list() # Creates empty list for plot data
      da.rt.region = list() # Creates empty list for plot data
      r.idx = 1 # Start the region name index at 1
      z.idx = 1 # Start the zone name index at 1
    
      # Run the loop for each key period requested.
      for ( p in 1:n.periods ) {
        period.name = period.names[p]
      
        # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
        if (commit.dispatch.zone) {
          for ( z in 1:length(zone.names) ) {
              zone.name = zone.names[z]
              da.rt.zone[[z.idx]] = knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_zone.Rmd', period.name = period.name, zone.name = zone.name) 
              z.idx = z.idx + 1
          } 
        } else {da.rt.zone = 'Section not run according to input file.'}
        
        if (commit.dispatch.region) {  
          # Create a plot for each region.
          for ( r in 1:length(region.names) ) {
              region.name = region.names[r]
              da.rt.region[[r.idx]] = knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_region.Rmd', period.name = period.name, region.name = region.name)
              r.idx = r.idx + 1
          }
        } else {da.rt.region = 'Section not run according to input file.'}
        
      }
    
      # Reconstruct the plot data into a format that will be output into the HTML below
      if (commit.dispatch.zone)   { da.rt.zone = knit_child(text = unlist(da.rt.zone)) }
      if (commit.dispatch.region) { da.rt.region = knit_child(text = unlist(da.rt.region)) }

    }
  } else { da.rt.zone = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
         da.rt.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'}
  
} else { da.rt.zone = 'Section not run according to input file.'
         da.rt.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Zones
`r da.rt.zone`

***
### Regions
`r da.rt.region`
***


## 22. Generation comparison by Generator Type
```{r generation-comparison, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (compare.dispatch.region | compare.dispatch.zone) {
  
  source('source_scripts/compare/c_d_gen_comparison.R') # Call this R script which created the data needed for plotting.
  
  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('plot.data.all') ) {
    # Check to see if the right data is ready for plotting.
    if ( typeof(plot.data.all)=='character' ) {
      print('ERROR: cap_committed function not returning correct results.')
    } else {
  
      comp.gen.zone = list() # Creates empty list for plot data
      comp.gen.region = list() # Creates empty list for plot data
      r.idx = 1 # Start the region name index at 1
      z.idx = 1 # Start the zone name index at 1
    
      # Run the loop for each generator type requested.
      for ( type.name in da.rt.types ) {
      
        # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
        if (compare.dispatch.zone) {
          for ( z in 1:length(zone.names) ) {
              zone.name = zone.names[z]
              comp.gen.zone[[z.idx]] = knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_zone.Rmd', type.name = type.name, zone.name = zone.name) 
              z.idx = z.idx + 1
          } 
        } else {comp.gen.zone = 'Section not run according to input file.'}
        
        if (compare.dispatch.region) {  
          # Create a plot for each region.
          for ( r in 1:length(region.names) ) {
              region.name = region.names[r]
              comp.gen.region[[r.idx]] = knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_region.Rmd', type.name = type.name, region.name = region.name)
              r.idx = r.idx + 1
          }
        } else {comp.gen.region = 'Section not run according to input file.'}
        
      }
    
      # Reconstruct the plot data into a format that will be output into the HTML below
      if (compare.dispatch.zone)   { comp.gen.zone = knit_child(text = unlist(comp.gen.zone)) }
      if (compare.dispatch.region) { comp.gen.region = knit_child(text = unlist(comp.gen.region)) }

    }
  } else { comp.gen.zone   = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
           comp.gen.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'}
  
} else { comp.gen.zone   = 'Section not run according to input file.'
         comp.gen.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


### Zones
`r comp.gen.zone`

***
### Regions
`r comp.gen.region`
***


