---
title: "Multi-area Grid Metrics Analyzer Comparison Plots"
author: "Created by: `r Sys.info()['user']`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path=fig.path.name, dev='png', fig.width=12)

# Set dynamic height for figure in regional generation chunk
if (exists('zone.names') { z.height = ( length(zone.names) %/% 3 + length(zone.names) %% 3 ) * 5
  } else { z.height = 5 }
if (exists('region.names') { r.height = ( length(region.names) %/% 3 + length(region.names) %% 3 ) * 5
  } else {r.height = 5 }
if (exists('reserve.names') { res.height = ( length(reserve.names) %/% 2 + length(reserve.names) %% 2 ) * 5
  } else { res.height = 5 })
s.height = ( length(db.loc) ) * 6
p.height = ( length(period.names) %/% 2 + length(period.names) %% 2 ) * 5
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Data below generated for:
"`r gsub('.*Model', 'Model', db$filename)`"

***
## Annual Dispatch Stacks 
***
## 1. Generation Differences
```{r gen-diff-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_diff_gen_stack.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 2. Zonal Generation
```{r zone-gen-diff-stacks, fig.height=z.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_zone_gen_stacks.Rmd')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 3. Regional Generation
```{r region-gen-diff-stacks, fig.height=r.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_region_gen_stacks.Rmd')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 4-6. Specified Period Dispatch Stacks
``` {r key-period-dispatch, cache=FALSE, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (key.period.dispatch.total.log | key.period.dispatch.zone.log | key.period.dispatch.region.log){  
  if (length(period.names)>0) {

    # Call interval_gen function and proces data for plots
    source('source_scripts/d_key_period_dispatch.R')

    # As long as the file exists (previous source found the R script) this loop runs
    if ( exists('key.period.gen') ) {
    # Check to see if the right data is ready for plotting.
      if ( typeof(key.period.gen)=='character' ) {
        key.period.dispatch.total  = 'ERROR: interval_gen function not returning correct results.'
        key.period.dispatch.zone   = 'ERROR: interval_gen function not returning correct results.'
        key.period.dispatch.region = 'ERROR: interval_gen function not returning correct results.'
      } else {
        # Check if total database info was selected in input file.
        if (key.period.dispatch.total.log) {
          key.plots.total = lapply(period.names, function(p){
                                   knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_total.Rmd',  
                                               period.name = period.name)
                                   })
          key.period.dispatch.total = knit_child(text = unlist(key.plots.total))
        } else {key.period.dispatch.total  = 'Section not run according to input file.'}
        
        # Check if zonal dispatch stacks were selected in input file.
        if (key.period.dispatch.zone.log) {
          plot.zones = zone.names[!zone.names %in% ignore.zones]
          key.plots.zone = mapply(function(k,z){ 
                                  knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_zone.Rmd', 
                                              period.name = p, zone.name = z)}, 
                                  rep(period.names,length(plot.zones)), rep(plot.zones,each=n.periods))
          key.period.dispatch.zone = knit_child(text = unlist(key.plots.zone))
        } else {key.period.dispatch.zone   = 'Section not run according to input file.'}
        
        # Check if regional dispatch stacks were selected in input file.
        if (key.period.dispatch.region.log) {
          plot.regions = region.names[!region.names %in% ignore.regions]
          key.plots.region = mapply(function(k,r){
                                    knit_expand(file = 'source_scripts/compare/c_p_key_period_dispatch_region.Rmd', 
                                                period.name = p, region.name = r)}, 
                                    rep(period.names,length(plot.regions)), rep(plot.regions,each=n.periods))
          key.period.dispatch.region = knit_child(text = unlist(key.plots.region))
        } else {key.period.dispatch.region = 'Section not run according to input file.'}
      }
    } else { key.period.dispatch.total  = 'Problem sourcing or running d_key_period_dispatch.R.'
             key.period.dispatch.zone   = 'Problem sourcing or running d_key_period_dispatch.R.'
             key.period.dispatch.region = 'Problem sourcing or running d_key_period_dispatch.R.' }
  } else { key.period.dispatch.total  = 'You didnt specify key periods. Cannot run this section.'
           key.period.dispatch.zone   = 'You didnt specify key periods. Cannot run this section.' 
           key.period.dispatch.region = 'You didnt specify key periods. Cannot run this section.' }
} else { key.period.dispatch.total  = 'Section not run according to input file.'
         key.period.dispatch.zone   = 'Section not run according to input file.' 
         key.period.dispatch.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Total
`r key.period.dispatch.total`

***
### Zones
`r key.period.dispatch.zone`

***
### Regions
`r key.period.dispatch.region`


***
## 7-9. Curtailment
***
### 7. Total Curtailment Difference
```{r yearly-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (curtailment.diff.table) {
  if ( typeof(total.generation)=='character' ) {
    print('ERROR: total.generation has errors. Cannot run this section.')
  } else if ( typeof(total.avail.cap) == 'character' ) { 
    print('ERROR: total.avail.cap has errors. Cannot run this section.')
  } else{
    # Run the cost query function
    curt.diff = tryCatch( curtailment_diff(total.generation, total.avail.cap), 
                          error = function(cond) { return('ERROR: curtailment diff function not returning correct results.') })
    kable(curt.diff, format.args = list(big.mark = ','), digits=2)
  }
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 8. Daily Curtailment Difference
```{r daily-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_daily_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 9. Interval Curtailment Difference
```{r interval-curtailment-diff}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source('source_scripts/compare/c_p_interval_curtailment.R')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 10. Total Cost Differences
```{r annual-cost-difference-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.cost.table & length(db.loc)>1) {
  # Run the cost query function
  cost.diff.table = tryCatch( costs_diff(total.emissions.cost, total.fuel.cost, total.ss.cost, total.vom.cost), 
                              error = function(cond) { return('ERROR: costs function not returning correct results.') })
  kable(cost.diff.table, format.args = list(big.mark = ',')) 
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 12. Region and Zone Info (GWh)
``` {r region-zone-flow-diff-tables}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 13. Interface Flow Table
```{r interface-flow-diff-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 14. Interface Flow Plots
```{r interface-flow-diff-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 16-17. Reserves
***
### 16. Annual Reserve Shortage by Scenario
```{r annual-reserves-scen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (annual.res.short.table) {
  # Run the cost query function
  res.short.table = tryCatch( annual_reserves_short(total.reserve.provision, total.reserve.shortage), 
                              error = function(cond) { return('ERROR: reserve function not returning correct results.') })
  kable(res.short.table, format.args = list(big.mark = ','))
} else { print('Section not run according to input file.') }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
### 17. Reserve Provisions by generator type
```{r reserves-stacks, fig.height=res.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source("source_scripts/compare/c_p_reserves_stack.R")
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 20. Region Price Duration Curves
```{r price-duration-curve-scen, fig.height=r.height}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
source("source_scripts/compare/c_p_price_duration_curve.R")
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## 21. DA-RT Committment and Dispatch Plots
```{r committment-dispatch, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (commit.dispatch.region | commit.dispatch.zone) {
  if (length(da.rt.types)>0) {
    source('source_scripts/d_DA_RT_commit_dispatch.R') # Call this R script which created the data needed for plotting.
    
    # As long as the file exists (previous source found the R script) this loop runs
    if ( exists('plot.data.all') ) {
      # Check to see if the right data is ready for plotting.
      if ( typeof(plot.data.all)=='character' ) {
        print('ERROR: cap_committed function not returning correct results.')
      } else {
        # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
        if (commit.dispatch.zone) {
          plot.zones = zone.names[!zone.names %in% ignore.zones]
          da.rt.zone = mapply(function(p,z){knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_zone.Rmd', 
                                                        period.name = p, zone.name = z)},
                              rep(period.names,length(plot.zones)), rep(plot.zones,each=n.periods))
          da.rt.zone = knit_child(text = unlist(da.rt.zone))
        } else {da.rt.zone = 'Section not run according to input file.'}
        
        # Create a plot for each region if selected.
        if (commit.dispatch.region) {  
          plot.regions = region.names[!region.names %in% ignore.regions]
          da.rt.region = mapply(function(p,r){knit_expand(file = 'source_scripts/compare/c_p_DA_RT_commit_dispatch_region.Rmd', 
                                                          period.name = p, region.name = r)},
                                rep(period.names,length(plot.regions)), rep(plot.regions,each=n.periods))
          da.rt.region = knit_child(text = unlist(da.rt.region))
        } else {da.rt.region = 'Section not run according to input file.'} 
      }
    } else if ( typeof(interval.da.committment) == 'character' ) { 
        da.rt.zone = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
      da.rt.region = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
    } else if ( typeof(interval.avail.cap) == 'character' ) { 
        da.rt.zone = 'INPUT ERROR: interval.avail.cap has errors. Cannot run this section.'
      da.rt.region = 'INPUT ERROR: interval.da.committment has errors. Cannot run this section.'
    } else {   da.rt.zone = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
             da.rt.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.' }
  } else {   da.rt.zone = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.'
           da.rt.region = 'You didnt specify generation types for DA-RT plots. Plots cannot be created.' }
} else {   da.rt.zone = 'Section not run according to input file.'
         da.rt.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

### Zones
`r da.rt.zone`

***
### Regions
`r da.rt.region`
***


## 22. Generation comparison by Generator Type
```{r generation-comparison, include=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Check if this section was selected to run in the input file
if (compare.dispatch.region | compare.dispatch.zone) {
  
  source('source_scripts/compare/c_d_gen_comparison.R') # Call this R script which created the data needed for plotting.
  
  # As long as the file exists (previous source found the R script) this loop runs
  if ( exists('plot.data.all') ) {
    # Check to see if the right data is ready for plotting.
    if ( typeof(plot.data.all)=='character' ) {
      print('ERROR: cap_committed function not returning correct results.')
    } else {
      
      # Check if zonal DA-RT plots were selected in input file. If so create a plot for each zone
      if (compare.dispatch.zone) {
        comp.gen.zone = mapply(function(t,z){ knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_zone.Rmd', 
                                              type.name = type.name, zone.name = zone.name) },
                               rep(da.rt.types,length(zone.names)), rep(zone,names,each=length(da.rt.types)))
        comp.gen.zone = knit_child(text = unlist(comp.gen.zone))
      } else {comp.gen.zone = 'Section not run according to input file.'}
      
      # Create a plot for each region.
      if (compare.dispatch.region) {  
        comp.gen.region = mapply(function(t,z){ knit_expand(file = 'source_scripts/compare/c_p_key_period_gen_comparison_region.Rmd', 
                                              type.name = type.name, region.name = region.name) },
                               rep(da.rt.types,length(region.names)), rep(region,names,each=length(da.rt.types)))
        comp.gen.region = knit_child(text = unlist(comp.gen.region))
      } else {comp.gen.region = 'Section not run according to input file.'}
    }
  } else { comp.gen.zone   = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'
           comp.gen.region = 'Problem sourcing or running d_DA_RT_commit_dispatch.R.'}
  
} else { comp.gen.zone   = 'Section not run according to input file.'
         comp.gen.region = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


### Zones
`r comp.gen.zone`

***
### Regions
`r comp.gen.region`
***


