---
title: "PLEXOS Run General Analysis"
author: 'MO'
date: "April, 2016"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
yr.data.generator      = tryCatch( yr_gen_query(db), error = function(cond) { return('ERROR') } )
yr.data.region         = tryCatch( yr_region_query(db), error = function(cond) { return('ERROR') } )
yr.data.zone           = tryCatch( yr_zone_query(db), error = function(cond) { return('ERROR') } )
yr.data.reserve        = tryCatch( yr_reserve_query(db), error = function(cond) { return('ERROR') } )
yr.data.interface.flow = tryCatch( yr_interface_query(db), error = function(cond) { return('ERROR') } )

if ( 5 %in% run.sections | 6 %in% run.sections | 7 %in% run.sections ) {
  int.data.generator     = tryCatch( int_gen_query(db), error = function(cond) { return('ERROR') } )
}

int.data.region        = tryCatch( int_region_query(db), error = function(cond) { return('ERROR') } )
int.data.interface     = tryCatch( int_interface_query(db), error = function(cond) { return('ERROR') } )
int.data.reserve       = tryCatch( int_reserve_query(db), error = function(cond) { return('ERROR') } )

r.z.load               = tryCatch( region_zone_load(db), error = function(cond) { return('ERROR') } )

# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=FALSE,
                      fig.path=fig.path.name, cache.path=cache.path.name, dev='png')
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Annual Dispatch Stacks 
***
## Total Generation
```{r total-gen-stack}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (1 %in% run.sections){
  total.gen.stack = knit_child('source_scripts/p_total_gen_stack.Rmd')
} else { total.gen.stack = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r total.gen.stack`

***
## Zonal Generation
```{r zone-gen-stacks}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (2 %in% run.sections) {
  zone.gen.stacks = knit_child('source_scripts/p_zone_gen_stacks.Rmd')
} else { zone.gen.stacks = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r zone.gen.stacks`

***
## Regional Generation
```{r region-gen-stacks}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# %%%%%%%%%%%%% *** Requires running "zone-gen-stacks" *** %%%%%%%%%%%%%%%%
if (3 %in% run.sections) {
  region.gen.stacks = knit_child('source_scripts/p_region_gen_stacks.Rmd')
} else { region.gen.stacks = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r region.gen.stacks`

***
## Individual Regions
```{r individual-region-stacks}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# %%%%%%%%%%%%%% *** Rquires running "region-gen-stacks" %%%%%%%%%%%%%%%%%%%%
if (4 %in% run.sections) {
  
if ( exists('region.gen.plot') ) {
# If the regional query didn't work, return an error. Else create plots.
if ( typeof(region.gen.plot)=='character' ) {
  print('ERROR: Zonal and regional query not returning correct results.')
} else {

    region.names = unique(region.gen.plot$Region) # List of all regions to make plots for
    key.plots = list() # Creates empty list for plot data

    # Create plot for each region in region.names
    for ( p in 1:length(region.names) )  {
      region.name = region.names[p]
      key.plots[p] = knit_expand(file = 'source_scripts/p_individual_region_stacks.Rmd', region.name=region.name)
    }

    # Reconstruct the plot data into a format that will be output into the HTML below
    individual.region.stacks = knit_child(text = unlist(key.plots))

  }
} else { individual.region.stacks = 'Region generation not found. Make sure "region-gen-stacks" chunk is running.' }
} else { individual.region.stacks = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r individual.region.stacks`

***
## Specified Period Dispatch Stacks
``` {r key-period-dispatch, cache=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (5 %in% run.sections){  

  # Call interval_gen function and proces data for plots
  source('source_scripts/d_key_period_dispatch.R')

if ( typeof(key.period.gen)=='character' ) {
  
} else {

  key.plots = list() # Creates empty list for plot data

  # Create data for each plot for the interesting periods
  for ( p in 1:n.periods ) {
    period.name = period.names[p]
    key.plots[[p]] = knit_expand(file = 'source_scripts/p_key_period_dispatch.Rmd', period.name = period.name)
  }

  # Reconstruct the plot data into a format that will be output into the HTML below
  key.period.dispatch = knit_child(text = unlist(key.plots))
}
} else { key.period.dispatch = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r key.period.dispatch`

***
## Curtailment
***
### Average Daily Curtailment
```{r yearly-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (6 %in% run.sections) {
  avg.year.curt = knit_child('source_scripts/p_yearly_curtailment.Rmd')
} else { avg.year.curt = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r avg.year.curt`

***
### Average Interval Curtailment
```{r daily-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# %%%%%%%%%% *** Requires running "yearly-curtailment" chunk *** %%%%%%%%%%%
if (7 %in% run.sections){
  avg.day.curt = knit_child('source_scripts/p_daily_curtailment.Rmd')
} else { avg.day.curt = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r avg.day.curt`

***
## Total Gen
```{r annual-generation-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# %%%%%%%%%% *** Requires running "total-gen-stack" chunk *** %%%%%%%%%%%%%%
if (8 %in% run.sections){
  annual.gen.table = knit_child('source_scripts/t_annual_generation.Rmd')
} else { annual.gen.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r annual.gen.table`

***
## Total Costs
```{r annual-cost-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (9 %in% run.sections) {
  annual.cost.table = knit_child('source_scripts/t_annual_cost.Rmd')
} else { annual.cost.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r annual.cost.table`

***
## Region and Zone Info (GWh)
``` {r region-zone-flow-tables}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (10 %in% run.sections) {
  region.zone.flow.tables = knit_child('source_scripts/t_region_zone_flow.Rmd')
} else { region.zone.flow.tables = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r region.zone.flow.tables`

***
## Zone Interface Flow
```{r zone-flow-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (11 %in% run.sections) {
  zone.flow.table = knit_child('source_scripts/t_zone_flow.Rmd')
} else { zone.flow.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r zone.flow.table`

***
```{r zone-flow-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# %%%%%%%%%% *** Requires running "zone-flow-table" chunk *** %%%%%%%%%%%%%%
if (12 %in% run.sections) {
  zone.flow.plots = knit_child('source_scripts/p_zone_interface_flow.Rmd')
} else { zone.flow.plots = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r zone.flow.plots`


***
```{r zonal-flow-plots}
if (13 %in% run.sections) {
# interchange.flows = tryCatch( interchange.flow(db), error=function(cond) {return('ERROR: Interface flows not found in query. Check initial setup file and PLEXOS outputs.')})

# for ( i in 1:n.periods) {
#   if (i==1) {  
#     plot.time = data.frame(time = seq(start.end.times$start[i], start.end.times$end[i], by = "1 hour"), Period = period.names[i]) 
#   } else {
#     plot.time = rbind(plot.time, data.frame(time = seq(start.end.times$start[i], start.end.times$end[i], by = "1 hour"), Period = period.names[i]))
#   }
# }
#     
# zonal.flows = zonal.flows %>%
#   join(plot.time, by = 'time') %>%
#   filter(time %in% plot.time$time)
# 
# key.plots = list()
# 
#   for ( p in 1:n.periods ) {
#     period.name = period.names[p]
#     key.plots[[p]] = knit_expand(file = '//plexossql/Data/moconnel/gtg/flow_plots.Rmd', period.name = period.name)
#   }
# 
#   # Reconstruct the plot data into a format that will be output into the HTML below
#   key.period.flow = knit_child(text = unlist(key.plots))


} else { key.period.flow = 'Section not run according to input file.' }
```


***
## Reserves
***
### Annual Reserve Provisions and Shortage
```{r annual-reserves-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (14 %in% run.sections) {
  annual.reserves.table = knit_child('source_scripts/t_annual_reserves.Rmd')
} else { annual.reserves.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r annual.reserves.table`

***
### Average Interval and Daily Reserve Provisions
```{r reserves-plots}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (15 %in% run.sections) {
  reserves.plots = knit_child('source_scripts/p_reserves.Rmd')
} else { reserves.plots = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r reserves.plots`

***
### Region and Zone Generation (GWh)
```{r region-zone-gen-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (16 %in% run.sections) {
  region.zone.gen.table = knit_child('source_scripts/t_region_zone_gen.Rmd')
} else { region.zone.gen.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r region.zone.gen.table`

***
### Capacity Factors
```{r capacity-factor-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
if (17 %in% run.sections) {
  capacity.factor.table = knit_child('source_scripts/t_capacity_factor.Rmd')
} else { capacity.factor.table = 'Section not run according to input file.' }
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```
`r capacity.factor.table`




